---
title: "Natural language processing Quiz 1"
author: "Shane Kao"
date: "Saturday, February 21, 2015"
output: pdf_document
---

```{r warning=FALSE}
setwd("C:/Users/asus/Downloads/final/en_US")
twitter=readLines("en_US.twitter.txt")
blogs=readLines("en_US.blogs.txt")
news=readLines("en_US.news.txt")
data=c(twitter,blogs,news)
```

# Question 1

The guy in front of me just bought a pound of bacon, a bouquet, and a case of

```{r warning=FALSE}
x="a case of"
data_v1=data[grep(x,data)]
n=length(data_v1)
pred=function(y){       
        data_v2=data_v1[grep(paste(x,y,sep=" "),data_v1)]
        length(data_v2)/n
}
candidate=c("soda","pretzels","cheese","beer")
prob=apply(cbind(candidate),1,pred)
output=data.frame("candidate"=candidate,"probability"=prob)
output[order(output$probability,decreasing=TRUE),]
```

# Question 2

You're the reason why I smile everyday. Can you follow me please? It would mean the

```{r warning=FALSE, echo=FALSE}
x="mean the"
data_v1=data[grep(x,data)]
n=length(data_v1)
pred=function(y){       
        data_v2=data_v1[grep(paste(x,y,sep=" "),data_v1)]
        length(data_v2)/n
}
candidate=c("world","most","universe","best")
prob=apply(cbind(candidate),1,pred)
output=data.frame("candidate"=candidate,"probability"=prob)
output[order(output$probability,decreasing=TRUE),]
```

# Question 3

Hey sunshine, can you follow me and make me the

```{r warning=FALSE, echo=FALSE}
x="make me the"
data_v1=data[grep(x,data)]
n=length(data_v1)
pred=function(y){       
        data_v2=data_v1[grep(paste(x,y,sep=" "),data_v1)]
        length(data_v2)/n
}
candidate=c("happiest","bluest","saddest","smelliest")
prob=apply(cbind(candidate),1,pred)
output=data.frame("candidate"=candidate,"probability"=prob)
output[order(output$probability,decreasing=TRUE),]
```

# Question 4

Very early observations on the Bills game: Offense still struggling but the

```{r warning=FALSE, echo=FALSE}
x="but the"
data_v1=data[grep(x,data)]
n=length(data_v1)
pred=function(y){       
        data_v2=data_v1[grep(paste(x,y,sep=" "),data_v1)]
        length(data_v2)/n
}
candidate=c("defense","crowd","referees","players")
prob=apply(cbind(candidate),1,pred)
output=data.frame("candidate"=candidate,"probability"=prob)
output[order(output$probability,decreasing=TRUE),]
```

# Question 5

Go on a romantic date at the

```{r warning=FALSE, echo=FALSE}
x="at the"
data_v1=data[grep(x,data)]
n=length(data_v1)
pred=function(y){       
        data_v2=data_v1[grep(paste(x,y,sep=" "),data_v1)]
        length(data_v2)/n
}
candidate=c("mall","grocery","movies","beach")
prob=apply(cbind(candidate),1,pred)
output=data.frame("candidate"=candidate,"probability"=prob)
output[order(output$probability,decreasing=TRUE),]
```

# Question 6

Well I'm pretty sure my granny has some old bagpipes in her garage I'll dust them off and be on my

```{r warning=FALSE, echo=FALSE}
x="be on my"
data_v1=data[grep(x,data)]
n=length(data_v1)
pred=function(y){       
        data_v2=data_v1[grep(paste(x,y,sep=" "),data_v1)]
        length(data_v2)/n
}
candidate=c("phone","motorcycle","way","horse")
prob=apply(cbind(candidate),1,pred)
output=data.frame("candidate"=candidate,"probability"=prob)
output[order(output$probability,decreasing=TRUE),]
```

# Question 7

Ohhhhh #PointBreak is on tomorrow. Love that film and haven't seen it in quite some

```{r warning=FALSE, echo=FALSE}
x="quite some"
data_v1=data[grep(x,data)]
n=length(data_v1)
pred=function(y){       
        data_v2=data_v1[grep(paste(x,y,sep=" "),data_v1)]
        length(data_v2)/n
}
candidate=c("thing","weeks","time","years")
prob=apply(cbind(candidate),1,pred)
output=data.frame("candidate"=candidate,"probability"=prob)
output[order(output$probability,decreasing=TRUE),]
```

# Question 8

After the ice bucket challenge Louis will push his long wet hair out of his eyes with his little

```{r warning=FALSE, echo=FALSE}
x="his little"
data_v1=data[grep(x,data)]
n=length(data_v1)
pred=function(y){       
        data_v2=data_v1[grep(paste(x,y,sep=" "),data_v1)]
        length(data_v2)/n
}
candidate=c("eyes","ears","fingers","toes")
prob=apply(cbind(candidate),1,pred)
output=data.frame("candidate"=candidate,"probability"=prob)
output[order(output$probability,decreasing=TRUE),]
```

# Question 9

Be grateful for the good times and keep the faith during the

```{r warning=FALSE, echo=FALSE}
x="during the"
data_v1=data[grep(x,data)]
n=length(data_v1)
pred=function(y){       
        data_v2=data_v1[grep(paste(x,y,sep=" "),data_v1)]
        length(data_v2)/n
}
candidate=c("sad","hard","worse","bad")
prob=apply(cbind(candidate),1,pred)
output=data.frame("candidate"=candidate,"probability"=prob)
output[order(output$probability,decreasing=TRUE),]
```

# Question 10

If this isn't the cutest thing you've ever seen, then you must be

```{r warning=FALSE, echo=FALSE}
x="must be"
data_v1=data[grep(x,data)]
n=length(data_v1)
pred=function(y){       
        data_v2=data_v1[grep(paste(x,y,sep=" "),data_v1)]
        length(data_v2)/n
}
candidate=c("asleep","insensitive","insane","callous")
prob=apply(cbind(candidate),1,pred)
output=data.frame("candidate"=candidate,"probability"=prob)
output[order(output$probability,decreasing=TRUE),]
```